|

### 2023-05-10 manuscript/paper.Rmd
added middle initial

---
title: |
  |  \Large Stickle!
author: | 
  | \large Matthew Stuart \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1.1mm}
  | \normalsize Loyola University Chicago \vspace{-1.1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1.1mm}
  | \normalsize [`mstuart@luc.edu`](mailto:mstuart@luc.edu) \vspace{-1.1mm}
  |
  | \large Akhil Ghosh \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1.1mm}
  | \normalsize Loyola University Chicago \vspace{-1.1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1.1mm}
  | \normalsize [`aghosh@luc.edu`](mailto:aghosh@luc.edu) \vspace{-1.1mm}
  |
  | \large Yoel Stuart \vspace{-1.1mm}
  | \normalsize Department of Biology \vspace{-1.1mm}
  | \normalsize Loyola University Chicago \vspace{-1.1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1.1mm}
  | \normalsize [`ystuart@luc.edu`](mailto:ystuart@luc.edu) \vspace{-1.1mm}
  |
  | \large Gregory J. Matthews \vspace{-1.1mm}
  | \normalsize Center for Data Science and Consulting; Department of Mathematics and Statistics \vspace{-1.1mm}
  | \normalsize Loyola University Chicago \vspace{-1.1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1.1mm}
  | \normalsize [`gmatthews1@luc.edu`](mailto:gmatthews1@luc.edu) \vspace{-1.1mm}
abstract: |
  | Evewryone loves the stickle \vspace{2mm}
  | *Keywords*: Stickle
bibliography: references.bib
fontsize: 12pt
link-citations: true
linkcolor: cyan
urlcolor: cyan
output:
  pdf_document:
    df_print: kable
    number_sections: true
    keep_tex: true
header-includes:
 \usepackage{setspace}
 \setstretch{1.15}
 \usepackage{float}
 \floatplacement{figure}{t}
---

>>>>

---
title: |
  |  \Large Stickle!
author: | 
  | \large Matthew Stuart \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1.1mm}
  | \normalsize Loyola University Chicago \vspace{-1.1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1.1mm}
  | \normalsize [`mstuart1@luc.edu`](mailto:mstuart1@luc.edu) \vspace{-1.1mm}
  |
  | \large Akhil Ghosh \vspace{-1.1mm}
  | \normalsize Department of Mathematics and Statistics \vspace{-1.1mm}
  | \normalsize Loyola University Chicago \vspace{-1.1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1.1mm}
  | \normalsize [`aghosh@luc.edu`](mailto:aghosh@luc.edu) \vspace{-1.1mm}
  |
  | \large Yoel E. Stuart \vspace{-1.1mm}
  | \normalsize Department of Biology \vspace{-1.1mm}
  | \normalsize Loyola University Chicago \vspace{-1.1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1.1mm}
  | \normalsize [`ystuart@luc.edu`](mailto:ystuart@luc.edu) \vspace{-1.1mm}
  |
  | \large Gregory J. Matthews \vspace{-1.1mm}
  | \normalsize Center for Data Science and Consulting; Department of Mathematics and Statistics \vspace{-1.1mm}
  | \normalsize Loyola University Chicago \vspace{-1.1mm}
  | \normalsize Chicago, IL 60660 \vspace{-1.1mm}
  | \normalsize [`gmatthews1@luc.edu`](mailto:gmatthews1@luc.edu) \vspace{-1.1mm}
abstract: |
  | Evewryone loves the stickle \vspace{2mm}
  | *Keywords*: Stickle
bibliography: references.bib
fontsize: 12pt
link-citations: true
linkcolor: cyan
urlcolor: cyan
output:
  pdf_document:
    df_print: kable
    number_sections: true
    keep_tex: true
header-includes:
 \usepackage{setspace}
 \setstretch{1.15}
 \usepackage{float}
 \floatplacement{figure}{t}
---
